---
title: "Big Team Collaboration on Data Management and Analysis with rOpenSci"
subtitle: "Big Team Science Conference 2025"
authors: "Liz Hare, Yanina Bellini Saibene"
institute: ""
date: "`r Sys.Date()`"
output: 
  xaringan::moon_reader:
    seal: false # false removes YAML title slide
    css: ['css/xaringan-themer.css', 'css/custom.css']
    nature: 
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
---

```{r metadata, echo=FALSE}
# creating HTML metadata to accompany the slides
# metathis package documentation: https://pkg.garrickadenbuie.com/metathis/

library(metathis)
meta() %>%
  meta_general(
    description = "Presentation Title",
    generator = "xaringan and remark.js"
  ) %>% 
  # GitHub repo housing the slides for the talk
  meta_name("github-repo" = "LizHareDogs/BTScon2025") %>%
  # metadata for the social card that appears when you share the link on social media
  meta_social(
    title = "BTScon2025 | Liz Hare & Yanina Bellini Saibene",
    url = "slide url",
    image = "coverImageSlide.png",
    image_alt = "",
    og_type = "website",
    og_author = "Liz Hare & Yanina Bellini Saibene")
  
```

```{r xaringanthemer, echo=FALSE, warning=FALSE}
library(xaringanthemer)

# creating a custom CSS stylesheet using xaringanthemer
# xaringanthemer package documentation: https://pkg.garrickadenbuie.com/xaringanthemer/reference/style_duo_accent_inverse.html

style_duo_accent_inverse(
  primary_color = "#C6B78A",   # gold color from the logo (headers, inverse slides)
  secondary_color = "#C6B78A", # gold color (links and bold words)
  white_color = "#F5F5F5", # off-white color (text)
  black_color = "#14213D", # dark navy blue color (slide background)
  base_font_size = "25px",
  header_h1_font_size = "2.75rem",
  header_h2_font_size = "2.25rem",
  header_h3_font_size = "1.75rem",
  link_decoration = "underline",
  table_row_even_background_color = "#313C54", # lighter navy color
  inverse_link_color = "#14213D", # dark navy blue color
  code_highlight_color = "#ECECCE", # beige color
  header_background_content_padding_top = "5rem",
  footnote_position_bottom = "40px",
  outfile = "css/xaringan-themer.css",
  text_font_family = "Atkinson Hyperlegible",
  text_font_google = google_font("Atkinson Hyperlegible"),
  header_font_google = google_font("Atkinson Hyperlegible"),
  extra_css = list(
    # the following css styles the horizontal bars
    "hr" = list("color" = "#C6B78A",
                "content" = "''",
                "display" = "block",
                "border" = "none",
                "background-color" = "#C6B78A",
                "height" = "0.08em"),
    # the following css styles the list markers to apply the primary color
    "li::marker" = list("content" = "&#8226;",
                        "color" = "#C6B78A"))
)
```

```{r xaringanExtra, echo=FALSE, warning=FALSE, message=FALSE}
library(xaringanExtra)

# specifying xaringanExtra features
# xaringanExtra package documentation: https://pkg.garrickadenbuie.com/xaringanExtra/#/?id=xaringanextra

xaringanExtra::use_xaringan_extra(
  c("tile_view",   # enables an overview of the slide deck using letter "O"
    "slide_tone"   # enables audible tone for slide transitions
    )
  ) 
```


```{r setup, include=FALSE, eval = TRUE}
# loading libraries
library(fontawesome)    # icons for use alongside contact info

# turning off scientific notation
options(scipen = 999)

# setting knitr code chunk options
knitr::opts_chunk$set(collapse = TRUE,
                      fig.retina = 3,
                      cache = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      comment = NA,
                      dpi = 300,
                      fig.align = "center")
```




class: middle, title



### `r rmarkdown::metadata$title`
--- 

.pull-left[
#### `r rmarkdown::metadata$subtitle`
]

.pull-right[
#### `r rmarkdown::metadata$author` 
<br> [`r fa("github", a11y="sem")` @LizHareDogs](https://github.com/LizHareDogs)<br>
[`r fa("mastodon", a11y="sem")` @LizHare](https://fosstodon.org/@lizhare) <br>
[`r fa("envelope", a11y="sem")` LizHare@DogGenetics.com](mailto:LizHare@DogGenetics.com)
]


---
# Introductions and Perspectives



.pull-left[
###Yani

- add
- stuff
- here
]
-
.pull-right[
### Liz
quantitative genetics
- academic and academic-adjacent
- usually  held rold or data person on tem so coded alone
joined ManyDogs Project, started thinking about collaborative coding
- rOpenSci Champions program enabled me to build skills for c
  collaborative coding
  ]
  
---
    
  #   What is [rOpenSci](https://ropensci.org)

Tagline: 
** Transforming science through open data, software & 
reproducibility **

rOpenSci is a community of practice
- culture of open, reproducible research using shared data and
  reusable software
- build infrastructure for sharing and collaboration, both socially
  and technically 


---

# rOpenSci Areas of Focus

- software review
- Infrastructure
- Training and mentorship (and training for mentorship!)
- Multilingual publishing

---

# rOpenSci Community Resources

- [rOpenSci website](https://ropensci.org)
    - Friendly, detailed [Dev Guide](https://devguide.ropensci.org)
      containing
        - [Packaging Guide](https://devguide.ropensci.org) introducing
      R tools and practices
        - [Guide for
      Authors](https://devguide.ropensci.org/softwarereview_author.html)
      to lead you through the rOpenSci-specific process
	  - [Guide for Reviewers](https://devguide.ropensci.org/softwarereview_reviewer.html)


---

# More Resources

Code review happens on [GitHub]((https://github.com/ropensci)

Each package review happens in an issue, and some good first examples
are recommended in the Guide for Reviewers.

We use a [handy
template](https://devguide.ropensci.org/reviewtemplate.html) t

- provides structure for review
- checklist of items to review

---

# More resources

- Join the rOpenSci Slack when you start contributing
- check out the [rOPenSci Discussion
  Forum](https://discuss.ropensci.org)
      - might be better for longer questions or explanations than
        Slack
		
			
# Champions Program


---

# Champions Program Training

    - Code best practices
- Version control and collaboration with GitHub
- Writing packages
- Reviewing packages
- Organizing inclusive open science events

---

# Champions Program Features

- Community
- Mentoring
- Write a package or review one
- Outreach activity (blog post, webinar or workshop)		]
 ---

# Unexpected Benefits

- Learn new packages and functions
- Learn clearer and more efficient approaches
- Enjoy the puzzle of figuring out and following the authors' work
- Introduction to object-oriented data structures helped in a future
  project
  - Ways of collaborating apply to private consulting project
  
---
  
# Code Review and Big Team Science  
  

---		

#### Thank you! 

* BTSCon organizers
* Colleagues at The Turing Way
* UseR!2021 Organizing Committee



